PRIMUS: Quiescent Fraction as a Function of Environment and Redshift

### 2014-03-24 qfenv_paper/qf_environment.tex
Wilman et al 2010
 to motivate choice in aperture radius and height

\subsection{Target Galaxy Samples} \label{sec:target} 
In this seciton we will define the target galaxy sample we use to compute the SMFs and QFs.
The population at $z \sim 0.5$ is derived from the PRIMUS data and the population at $z \sim 0.1$ is derived from the SDSS data, both described above.
For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and then impose magnitude limits on optical selection bands as specified in 
\cite{Moustakas:2013aa} Table 1.
These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
Next, we join the PRIMUS, {\em GALEX}, and IRAC window functions to construct the angular selection function.
We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
redshift range $0.2 - 0.8$.
Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift failures.
The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation (1) in \cite{Moustakas:2013aa}.
In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, apparent magnitude limit of the survey, and the typical stellar 
mass-to-light ratio of galaxies near the flux limit.

@@

\subsection{Galaxy Environment} \label{sec:environment}
In addition to the quiescent/star-forming classification, we now measure the environment for the target galaxy sample. 
First, we define the environment of a galaxy as the number of neighboring galaxies contained within a fixed aperture centered around it.
As our aperture, we use a cylinder with dimensions with $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and $H_{\rm{ap}} = 25 \; \rm{Mpc}/h$. 
Though spherical apertures are often used in literature (e.g. \cite{Croton:2005aa}), we use a cylindrical aperture in order to 
account for the PRIMUS redshift errors and redshift space distortions.  
Furthermore, we use a cylinder with the specified dimensions based on scale dependence for clustering analysis done in 
\cite{Blanton:2006aa}, which suggests that galactic properties such as star-formation histories are dependent on properties
 such as the masses of their host dark matter halos.
Hence, with cylindrical apertures of $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ we are able to probe the local small scale environment 
within the scales of the host dark matter halos.
We extend our analysis to cylindrical apertures with cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$; however 
we find that the variation in $R_{\rm{ap}}$ does not change our results significantly (difference in $f_{Q} < 0.05$). 
Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} for a mock galaxy catalogue generated from embedding 
galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}). 
%include a sentence that sums up everything in Croton and Muldrew? 
%Also include remarks on Wilman et al.

In order to measure environment using an aperture defined above, we first construct a volume limited 
{\em Environment Defining Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at each redshift bin. 
The $M_{r}$ cut-offs are selected so that the cumulative number density over $M_{r}$ at all redshift bins are equal. 
By equating the cumulative number densities at different redshifts not only can we reasonably compare the 
environment values at different redshift bins but we also attempt to build an EDP that has a similar galaxy 
population in all of the redshift bins i.e. accounts for the progenitor bias. 
As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find in their analysis of the cumulative number density 
method using a dark matter simulation with abundance matching and a semi-analytic model, respectively, 
the cumulative number density method, while it does not precisely account for the scatter in mass accretion or 
galaxy-galaxy mergers, provides a reasonable means to compare galaxy populations over a wide range of cosmic time. 
Furthermore \cite{Behroozi:2013aa} %%%FINISH THIS SENTENCE

To construct the EDP for the PRIMUS (hereafter PRIMUS EDP) we use the same PRIMUS data as the 
target galaxies, described in Section \ref{sec:target}. 
We restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$. 
Before we consider the cumulative number densities in these bins, we first determine $M_r$ limit for the 
highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ 
and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ 
have fewer galaxies than the bin at $M_{r, \rm{lim}}$. 
We choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be, conservatively, $M_{r} = -20.75$. 
For the other redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such 
that the cumulative number density of the bin ordered by $M_{r}$ is equal to the cumulative 
number density of the highest redshift bin. 
The cumulative number density calculations accounts for the statistical weights of the galaxies (Section 
\ref{sec:primus} and \ref{sec:sdss}).

For the EDP of the SDSS-{\em GALEX} sample (hereafter SDSS EDP), we do not use the parent data of 
the SDSS-{\em GALEX} target sample the geometry of the combined angular selection function of the 
SDSS VAGC and {\em GALEX}. 
Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP
to the entire SDSS VAGC to include galaxies outside of the {\em GALEX} window function. 
Furthermore, we impose a redshift range of $0.0375-0.145$ on the SDSS EDP. 
This redshift range is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at 
$z \sim 0.01$ in the SDSS VAGC data.  
The lower bound for the redshift range was empirically determined by the bright limit and the upper bound 
by the faint limit of the $M_{r}$ versus redshift distribution. 
The same fixed cumulative number density method, described above, is used on this SDSS EDP to equate
the cumulative number density of SDSS EDP to the highest redshift bin of the PRIMUS EDP. 
Ultimately, we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.06-0.145$, 
$0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively.  %%%% PUT NEW VALUES
These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots $M_{r}$ distribution as 
a function of redshift for the EDP (red) and the target galaxy sample (black).

>>>>

\subsection{Target Galaxy Sample} \label{sec:target} 
In this seciton we will define the target galaxy sample we use to compute the SMFs and QFs.
The population at $z \sim 0.5$ is derived from the PRIMUS data and the population at $z \sim 0.1$ is derived from the SDSS data, both described above.
For the intermediate redshift target galaxy population, we begin with the selection criteria imposed in \cite{Moustakas:2013aa} for its parent sample.
We take the statistically complete {\em primary} sample from the PRIMUS data (\cite{Coil:2011aa}) and then impose magnitude limits on optical selection bands as specified in 
\cite{Moustakas:2013aa} Table 1.
These limits are in different optical selection bands and have different values for our five PRIMUS target fields.
Next, we join the PRIMUS, {\em GALEX}, and IRAC window functions to construct the angular selection function.
We then exclude stars and broad-line AGN to only select objects spectroscopically classified as galaxies, with high-quality spectroscopic redshifts ($Q \geq 3$) within the 
redshift range $0.2 - 0.8$.
Afterwards we assign statistical weights (described in \cite{Coil:2011aa} and \cite{Cool:2013aa}) to the objects in order to correct for targeting incompleteness and redshift failures.
The statistical weight, $w_i$, for each galaxy is given by
\begin{equation}
w_{i} = (f_{\rm{target}} \times f_{\rm{collision}} \times f_{\rm{success}})^{-1},
\end{equation}
Equation (1) in \cite{Moustakas:2013aa}.
In addition to the selection criteria above, we impose stellar mass limits to have a stellar mass complete sample.  
Stellar mass completeness limits for a magnitude-limited survey such as PRIMUS is a function of redshift, apparent magnitude limit of the survey, and the typical stellar 
mass-to-light ratio of galaxies near the flux limit.

@@

\subsection{Galaxy Environment} \label{sec:environment}
In addition to the quiescent/star-forming classification, in this section, 
we measure the environment for our target galaxies. We define the 
environment of a galaxy as the number of neighboring galaxies 
contained within a fixed aperture centered around it. We use a fixed 
aperture environment because, as \cite{Muldrew:2012aa} finds in 
their comparison of different environment definition using simulations, 
it provides a better probe of the entire halo in comparison to other 
environment definitions such as nearest neighbor, which provides 
a better tracer at inter-halo scales. For our aperture, 
we use a cylinder of dimensions: $R_{\rm{ap}} = 2 \; \rm{Mpc}/h$ and 
$H_{\rm{ap}} = 25 \; \rm{Mpc}/h$. Though spherical apertures are 
often used in literature (e.g. \cite{Croton:2005aa}), we use a 
cylindrical aperture in order to account for the PRIMUS redshift errors 
and redshift space distortions (i.e. "Finger of God" effect). \cite{Cooper:2005aa} 
finds that $\pm 1000 \; \rm{km} \rm{s^{-1}}$ optimally reduces the 
effects of redshift space distortions and PRIMUS $\sigma_z \sim 
0.0085$ at $z \sim 0.7$, so aperture height of $25 \; \rm{Mpc}/h$ 
successfully accounts for both of these effects. Furthermore, our 
choice of cylinder radius was motivated by scale dependence 
analyses in literature (\cite{Blanton:2006aa}, \cite{Wilman:2010aa}, 
and \cite{Muldrew:2012aa}), which suggest that galactic properties 
such as color and quenched fractions are dependent on halo-scale 
properties such as host dark matter halo mass. \cite{Wilman:2010aa}, 
which uses environment defined by annuli of different radii, find 
positive correlation for quenched fraction and color on scales 
$< 1 \; \rm{Mpc}$ and anti-correlation on scales $> 3 \; \rm{Mpc}$. 
Our choice of $2 \rm{Mpc}/h$ provides sufficient sample size of 
galaxies in dense environments, for robust statistics, while 
tracing galactic properties within the halo scale. When we extend our 
analysis to cylindrical apertures with $R_{\rm{ap}} = 1 \; \rm{Mpc}/h$, 
we find that the change in $R_{\rm{ap}}$ does not significantly change 
our results (difference in $f_{Q} < 0.05$). 
%Similar fixed aperture methods have also been used in \cite{Croton:2005aa} for galaxies in the 2dF Galaxy Redshift 
%Survey (\cite{Colless:2003aa}) and in \cite{Muldrew:2012aa} for a mock galaxy catalogue generated from embedding 
%galaxies onto the Millenium Dark Matter Simulation (\cite{Springel:2005aa}).

With proper motivation for the fixed aperture environment definition, 
we now proceed to measuring the environment for our target galaxies. 
First, we construct a volume limited {\em Environment Defining 
Population} (EDP) with absolute magnitude cut-offs ($M_{r}$) at 
each redshift bin. EDP galaxies within the aperture surrounding each 
target galaxy are the neighboring galaxies in our definition of 
environment. The $M_{r}$ cut-offs for the EDP are selected so that 
the cumulative number density over $M_{r}$ at all redshift bins are 
equal. Not only does this provide a reasonably comparison of the 
environment measurements at different redshifts but it also seeks 
to construct an EDP that contains similar galaxy populations 
throughout our redshift range (i.e. to account for the progenitor bias 
in our EDP). As \cite{Behroozi:2013aa} and \cite{Leja:2013aa} find 
in their analysis of the cumulative number density method, the 
cumulative number density method, though it does not precisely 
account for the scatter in mass accretion or galaxy-galaxy mergers, 
provides a reasonable means to compare galaxy populations over 
a wide range of cosmic time.

In constructing the EDP for the PRIMUS (hereafter PRIMUS EDP) we use the same PRIMUS data as the 
target galaxies, described in Section \ref{sec:target}. 
We restrict the PRIMUS galaxies to $0.2 < z < 0.8$ and divide them into bins of $\Delta z = 0.2$. 
Before we consider the cumulative number densities in these bins, we first determine $M_r$ limit for the 
highest redshift bin ($0.6-0.8$) by examining the $M_{r}$ distribution with bin size $\Delta M_{r} = 0.25$ 
and select $M_{r,\rm{lim}}$ near the peak of the distribution where bins with $M_{r} > M_{r,\rm{lim}}$ 
have fewer galaxies than the bin at $M_{r, \rm{lim}}$. 
We choose $M_{r, \rm{lim}}(0.6 < z < 0.8)$ to be, conservatively, $M_{r} = -20.75$. 
For the other redshift bins, we impose absolute magnitude limits ($M_{r,\rm{lim}}$) such 
that the cumulative number density of the bin ordered by $M_{r}$ is equal to the cumulative 
number density of the highest redshift bin. 
The cumulative number density calculations accounts for the statistical weights of the galaxies (Section 
\ref{sec:primus} and \ref{sec:sdss}).

For the SDSS-{\em GALEX} EDP (hereafter SDSS EDP), we do not use the parent data of 
the SDSS-{\em GALEX} target sample which uses the geometry of the combined angular selection function of the 
SDSS VAGC and {\em GALEX}. 
Instead, since FUV, NUV values are not necessary for EDP, we extend the parent data of the SDSS EDP
to the entire SDSS VAGC, including galaxies outside of the {\em GALEX} window function. 
Furthermore, we impose a redshift range of $0.0375-0.145$ on the SDSS EDP. 
This redshift range is due to the lack of faint galaxies at $z \sim 0.2$ and the lack of bright galaxies at 
$z \sim 0.01$ in the SDSS VAGC data.  
The lower bound for the redshift range was empirically determined by the bright limit and the upper bound 
by the faint limit of the $M_{r}$ versus redshift distribution. 
The same fixed cumulative number density method, described above, is used on this SDSS EDP to equate
the cumulative number density of SDSS EDP to the highest redshift bin of the PRIMUS EDP. 
Ultimately, we get $M_{r,\rm{lim}} = -20.57$, $-20.73$, $-20.80$ and $-20.95$ for the redshift bins $0.06-0.145$, 
$0.2-0.4$, $0.4-0.6$, $0.6-0.8$, respectively.  %%%% PUT NEW VALUES
These absolute magnitude limits are illustrated in Figure \ref{fig:targetEDP}, which plots $M_{r}$ distribution as 
a function of redshift for the EDP (red) and the target galaxy sample (black).
